Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2022-09-06 ba_resubmit/response_to_reviewers.tex

	\begin{enumerate}
	\item There are problems with the notation, which in places is not defined, in others is used before being defined, and in others yet is used inconsistently. For example, $I_obs()$ is never defined, $n_12(Z)$ first appears on p. 5, but is not defined (in passing) until the bottom of p. 7, and it seems to become D on p. 8.
	\item Throughout the manuscript, $n_1$ and $n_2$ are used interchangeably with $n_A$ and $n_B$, sometimes in the same section, as it happens, for example, in Section 3.1.
	\item The loss function on p. 9 is out of Sadinle’s paper and it inherits the typo therein $(\theta_11, if Z_j, \hat{Z_j}, \ldots)$.
	\item  In the statement of Lemma 1 on p.13, B comes out of nowhere.  (Thinking I had missed something, I went back to the previous pages only to find out that B would be then defined in the proof.)
	\item Formatting of all displayed math must be checked and fixed, especially as far as punctuation is concerned, as commas seem to be missing in multiple places. For example, in Equation (1), there should be a comma after 0 and after 1, and this is by no means an isolated occurrence.
	\end{enumerate}
	}

\reply{%
	We thank the Editor, the AE, and the reviewer for their feedback. We have made an effort to make it more clear our contributions in this work as opposed to previous work. Furthermore, we have carefully edited the paper to address issues that were pointed out by the Editorial Board.

		\begin{enumerate}
		\item \textcolor{red}{We have included a discussion of our missingness assumptions and the definition of $I_{obs}()$ near the end of Section 3.}

@@

	\reply{%
	We thank the reviewer (AE) for noticing our computational novelties that expand upon the prior limitations of the prior work of Sadinle (2017). Our review paper clarifies our novel contributions, improves upon the exposition of the writing, provides a practical guidance for users, and expands the simulations. We expand on these points further below. \todo
	}

	\pointRaised{R1}{%
		Overall, the notation is, somewhat by necessity, quite extensive. However, I’m not convinced that it’s entirely consistent. A glossary in the appendix may help the reader navigate the paper more easily.}
\reply{%
	\textcolor{blue}{I think this is an excellent idea and it could make sure that we don't miss anything. It would really help the reader. You could make a table of the notation, and Neil does this quite well in the Marchant 2021 paper as an example.}
}

\pointRaised{R1}{%
	Section 2, line 1: It may help to explicitly define X1 and X2 as being vectors of indices as implied by equations (1) and (2).
}
\reply{
	\textcolor{red}{I'm not sure the best way to approach this. Here are two options:}

	\textcolor{red}{OPTION 1: Consider two databases $X_1$ and $X_2$ containing records $\{x_{1i}\}_{i=1}^{n_1}$ and $\{x_{2j}\}_{j=1}^{n_2}$ respectively. Without loss of generality, denote files such that $n_1 \geq n_2$. We follow the convention established by Sadinle (2017) and say ``record i $\in X_1$" rather than the more compact $x_{1i}$ in order to avoid double subscripts.}

@@

%\textcolor{blue}{This is a good point. I wonder if we could perhaps remove a lot of the notation by Sadinle/FS and redo the notation such that the ordering wouldn't matter. Also, it would make more sense to follow with the examples that we use in the paper -- NLTCS and EL Salvador so that we don't confuse the reader. Let's talk through this point as this would be a big change. If the algorithm and notation can be easily modified to reverse things, this would be a nice addition to the paper and improvement over Sadinle.}

\pointRaised{R1}{%
5. Section 3, full model: $I_obs(.)$ seems to be taken from a different paper dealing with missing fields, which is not at all discussed in this manuscript. This consideration of missing fields and the accompanying discussion of missing data mechanism should be included if such data is to be considered for this manuscript. This comment also applies to the $Gamma^{obs}$ notation in the following subsection.
}

\reply{%
	\textcolor{red}{We have included a discussion of our missingness assumptions and the definition of $I_{obs}()$ near the end of Section 3.}
}

@@

\pointRaised{R1}{%
	Section 3, full model: The square brackets seem to be misplaced, as the exponent includes indices of the sum contained in the brackets.
}

\reply{%
	We thank the reviewers for identifying this oversight, and have corrected the expression.
}

\pointRaised{R1}{%
Section 3.1, I found the motivational descriptions in this section to be somewhat confusing, in that they seem to mix the posterior behavior (e.g., parameters are updated though standard multinomial-Dirichlet…) and model construction (as a function of pi, Z is a series of successes…). This subsection might be easier to understand if its purpose was more bluntly described in an opening sentence or paragraph and streamlined to focus only on the full conditional distributions for a Gibbs Sampler. In addition, the mixed motivation may have led to errors in intermediate conclusions. In particular, the derivation of the probability of $\Gamma_{.j}$ seems to be missing a factor of $u_{fl}^I(gamma_{ij}^f=l)$. This is not important to the eventual full conditional of Z, but does not seem to be correct for the distribution of Gamma as claimed.
}

\reply{%
\textcolor{red}{\todo We should meet specifically to talk about how to best present the Gibbs Sampler. I think it be good to move as much of it as possible (at least the messy math and derivations) into the appendix.}

@@

\pointRaised{R1}{%
	Section 5.2 and 5.3 simulations – are these a single simulated datasets? Do these same results hold over multiple simulated datasets, Or was this just a chance result for each setting?
}

\reply{%
	In the caption under Figure 3, we explain that we have 100 pairs of sets of records for each level of overlap and error. Thus the table represents results over 900 pairs of datasets. We have added this description in the body of the paper as well for clarity. 
}

\pointRaised{R1}{%
Section 5.3 simulation – RR results are not presented.
}

\reply{%
	\textcolor{red}{We have updated the image with these results. Since its is presented along side NPV and PPV, for which values close to 1 indicate strong performance, we have presented decision rate (DR) results.}
}

### 2022-09-06 ba_resubmit/kundinger_resubmit.tex
Added RR to plot, many edits

Lastly, we note that it is common to encounter missing information in datasets used for record linkage. Whether information is missing in record $i \in \bf{X}_1$ or $j \in \bf{X}_2$, the comparison vector $\bf{\gamma}_{ij}$ will have missing values. We handle this issue by assuming that this missingness occurs at random (MAR, by \cite{LittleRubin2002})

@@

%The model can then be specified as follows:
With the \texttt{fabl} prior defined, we present the full model as follows:

@@

	We note here that the implementation of \texttt{BRL} that we use is coded in C \citep{sadinle_bayesian_2017}.  In contrast, we use non-optimized code written in R for \texttt{fabl}.  While this complicates comparisons, and indeed disfavors fabl, the computational speed gains for \texttt{fabl} are still evident, especially for larger sample sizes.  Additionally, although \texttt{fabl} is amenable to parallelization, this simulation was run on a single core. Implementing \texttt{fabl} in C++ with paralellization for the hashing step and sampling the matching status of the record pairs should lead to even more computational gains.

@@

	By leaving $\theta_{10} = \theta_{01} = 1$ and $\theta_{11} = 2$, but setting $\theta_R = 0.1$, we allow the model to decline to decide a match for certain records, with nonassignment being 10\% as costly as a false match. In this context, we are no longer focused on finding all true matches, but rather protecting against false matches. Thus, instead of recall, we use the negative predictive value (NPV), defined as the proportion of non-links that are actual non-matches. Mathematically, $\text{NPV} = \sum_{j=1}^{n_2} I(\hat{Z}_j = Z_j = n_1 + j)$/$\sum_{j=1}^{n_2} I(\hat{Z}_j = n_1 + j)$. We continue to use the precision, which is renamed the positive predictive value (PPV) in this context. Lastly, we also report the rejection rate (RR), or how often the model declines to make a linkage decision, defined as RR = $\sum_{j=1}^{n_2} I(\hat{Z}_j = R)$.

@@

	\begin{figure}[t]
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot_partial} 
			\caption{Negative predictive value (NPV) and positive predictive value (PPV) on simulated datasets. We see poorer performance for \texttt{fabl} only in situations with high overlap.}
			\label{fig:sadinle_simulation_partial}
		\end{center}
	\end{figure}

@@

			\Procedure{Gibbs Sampling}{}
			\State Initialize $m$, $u$, and $Z$ parameters.

>>>>

\textcolor{red}{Lastly, we note that it is common to encounter missing information in datasets used for record linkage. Whether information is missing in record $i \in \bf{X}_1$ or $j \in \bf{X}_2$, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. We handle this issue by assuming that this missingness occurs at random (MAR, by \cite{LittleRubin2002}). With this assumption, we can marginalize over the missing data, and do all computation simply using the observed data. To notate this, we use the indicator $I_{obs}(\cdot)$, which takes on the value 1 when the argument inside the parentheses is observed, and 0 otherwise.}

@@

%The model can then be specified as follows:
With the \texttt{fabl} prior defined and our missingness assumptions addressed, we present the full model as follows:

@@

	We note here that the implementation of \texttt{BRL} that we use is coded in C \citep{sadinle_bayesian_2017}.  In contrast, we use non-optimized code written in R for \texttt{fabl}.  While this complicates comparisons, and indeed disfavors \texttt{fabl}, the computational speed gains for \texttt{fabl} are still evident, especially for larger sample sizes.  Additionally, although \texttt{fabl} is amenable to parallelization, this simulation was run on a single core. Implementing \texttt{fabl} in C++ with paralellization for the hashing step and sampling the matching status of the record pairs should lead to even more computational gains.

@@

	By leaving $\theta_{10} = \theta_{01} = 1$ and $\theta_{11} = 2$, but setting $\theta_R = 0.1$, we allow the model to decline to decide a match for certain records, with nonassignment being 10\% as costly as a false match. In this context, we are no longer focused on finding all true matches, but rather protecting against false matches. Thus, instead of recall, we use the negative predictive value (NPV), defined as the proportion of non-links that are actual non-matches. Mathematically, $\text{NPV} = \sum_{j=1}^{n_2} I(\hat{Z}_j = Z_j = n_1 + j)$/$\sum_{j=1}^{n_2} I(\hat{Z}_j = n_1 + j)$. We continue to use the precision, which is renamed the positive predictive value (PPV) in this context. Lastly, we also examine the rejection rate (RR), or how often the model declines to make a linkage decision, defined as RR = $\sum_{j=1}^{n_2} I(\hat{Z}_j = R)/n_2$. \textcolor{red}{To convey this information alongside NPV and PPV, for which values close to 1 indicate strong performance, we report the decision rate (DR), defined as DR = $1 - RR$.}

	\textcolor{red}{Should I skip defining RR? And just define decision rate DR = $\sum_{j=1}^{n_2} I(\hat{Z}_j \neq R)/n_2$?}

@@

	\begin{figure}[t]
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot_partial_DR} 
			\caption{Negative predictive value (NPV), positive predictive value (PPV), and decision rate (DR) on simulated datasets. We see poorer performance for \texttt{fabl} only in situations with high overlap.}
			\label{fig:sadinle_simulation_partial}
		\end{center}
	\end{figure}

@@

			\Procedure{Gibbs Sampling}{}
			\State Initialize $\Phi$, and $Z$ parameters.
